\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-03-31 paper/main.tex
minor corrections in main.tex & plot-corr-of-regressors.py

A “no speech” regressor (“no-sp”; N=264) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech. Each event of the no speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no speech condition (s. anno2events-files.py). A length of 0.07s was chosen for these events matching the average length of phonemes.

>>>>

A “no-speech” regressor (“no-sp”; N=264) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech. Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no-speech condition (s. anno2events-files.py). A length of 0.07s was chosen for these events matching the average length of phonemes.
